---
title: "Milestone 5"
author: "Amy Zhou"
date: "3/20/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(janitor)
library(tidyverse)
library(readxl)
library(jsonlite)
library(lubridate)
library(readr)
library(data.table)
library(reprex)
```
```{r data_intake, include = FALSE, cache = TRUE}
north_carolina <- stream_in(xzfile("raw-data/North Carolina-20200302-xml/data/data.jsonl.xz")) 
save(north_carolina, file ="raw-data/north_carolina.Rdata")

```

```{r subset_data, echo = FALSE}


nc_subset <- north_carolina %>% 
  mutate(decision_date = as.Date(decision_date)) %>% 
  drop_na(decision_date) 



```
```{r plot, echo = FALSE}

north_carolina_plain <- north_carolina %>%
  select(!court)

court_data <- north_carolina$court %>% 
  rename(court_abbreviation = name_abbreviation, court_name = name, court_slug = slug, court_url = url, court_id = id)

north_carolina_new <- cbind(north_carolina_plain,court_data ) %>% 
  mutate(decision_date = as.Date(decision_date))




```

```{r}
north_carolina_new %>% 
  mutate(court_name = as.factor(court_name)) %>% 
  mutate(decision_date =  year(decision_date)) %>% 
  filter(court_name == "North Carolina Court of Appeals" |
           court_name == "Supreme Court of North Carolina") %>% 
  filter(decision_date > 1890) %>% 
  ggplot(aes(x = decision_date, fill = court_name)) +
  geom_bar() +
  labs(
    title = "Number of Cases in North Carolina Over Time",
    subtitle = "Officially Published Cases from 1890 to 2018",
    caption = "Data From the Library Innovation Lab's Case Law Project"
  ) +
  xlab(
    "Year"
  ) +
  ylab(
    "Case Count"
  ) +
  theme(
    legend.title = element_blank()
  )

# ggsave('amy_zhou_final_project_app/graphics/NC_case_count.png')
  
```




## Disclaimer:
This graph is a far simplified version of the graph I had earlier. Unfortunately after losing the csv I was working off of as well as the majority of my code, I was unable to manipulate the data as I had before (in the csv, the court dataframe column had been unnested so I could access the court names to court cases based on court). I tried to recreate the csv with write_csv, fwrite but ran into errors every time. I also tried to run unnest() also with no success. Thus I had to settle for just counting by year and not year and court. I am continuing to work on trying to figure out the csv or unnesting. 

I however, also reconstructed some of my previous code in the form of north_carolina.rmd. It is on my repo here if you would like to see: https://github.com/amyzhou9/gov1005-final-project

In this graph, you can see a steady increase in cases in the court system as might be expected. 








